Temperature Effects on Surface Sulfur Dioxide

### 2011-08-26 Coordination-Results.tex
Wrote an introduction, added paragraph about "why we need to talk about the cycle-signal bouncing and why it needs to be taken care of"

	Looking closer at the coordination types it is notable that coordinations lacking any sulfur interactions (i.e. ``O'', ``OO'', etc.) represent the least frequently formed bonding coordinations. A bonding coordination with at least a single sulfur interaction is clearly favored over \suldiox~``oxygen-only'' bonding to waters. In our previous classical simulations of \suldiox~on water we concluded that during adsorption and throughout the interface, the \suldiox orients so that its sulfur tends to the \wat~bulk side of the interface.\cite{Shamay2011} The coordination distributions here support the idea that binding through the sulfur is preferable, and to the extent that a non-sulfur coordination is rarely formed during the course of all our simulations.

>>>>

	Looking closer at the coordination types it is notable that coordinations lacking any sulfur interactions (i.e. ``O'', ``OO'', etc.) represent the least frequently formed bonding coordinations. A bonding coordination with at least a single sulfur interaction is clearly favored over \suldiox~``oxygen-only'' bonding to waters. In our previous classical simulations of \suldiox~on water we concluded that during adsorption and throughout the interface, the \suldiox~orients so that its sulfur tends to the \wat~bulk side of the interface.\cite{Shamay2011} The coordination distributions here support the idea that binding through the sulfur is preferable, and to the extent that a non-sulfur coordination is rarely formed during the course of all our simulations.

### 2011-08-26 Cycle-Results.tex
Wrote an introduction, added paragraph about "why we need to talk about the cycle-signal bouncing and why it needs to be taken care of"

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{Cyclic hydrate structures form throughout the MD simulations involving the \suldiox~and one or more water molecules. Shown here are the different cycles by number of water (up to 4), and their occurence rate as a percentage of the total simulation time. The far right part of the plot shows the contributions of the two types of triple-water cycles (see Figure \ref{fig:type-3-varieties}). The cycles had to meet the ``minimally-SO'' bonding criteria (at least one bond to the sulfur and one oxygen bond on the \suldiox) to be used in the analysis.}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}

@@

Knowing that the \suldiox~bound to a water surface is most likely in the ``SO'' bonding coordination, and also often taking part in some type of cyclic structure, how long does the cyclic hydrate form before breaking to an acyclic hydrate structure? To answer the questions of cyclic lifespans, a method was devised to define a lifetime of a cycle. For each trajectory, the coordinate data was analyzed to determine if a cyclic hydrate structure was formed based on the bonding distance criteria established earlier in this manuscript. A timeline was then produced where each timestep was given a value of 1 or 0 if a \suldiox~cycle was formed or not, respectively. This resulted in a time-function, $C(t)$, similar in nature to a digital signal. A representative portion of the resulting cycle formation time-function is plotted for one of the simulated trajectories shown as the dashed black line in Figure \ref{fig:debouncing}. At the far left of the plot the function is in the ``no cycle'' state, and then switches ``on'' as a cycle is formed later in time. The cyclic structure is very dynamic, constantly moving and distorting, so any of the bonds forming the cyclic bonding structure are liable to break and reform quickly. This is manifested in Figure \ref{fig:debouncing} as a series of very sharp spikes in the $C(t)$ function lasting less than 10 fs each. Because of the very rapid breaking and reformation of the cyclic structure, a procedure was used to debounce the time-function to disregard very brief moments when the cycle breaks or forms for less than 20 fs. The time-function, $C(t)$ was smoothed using a moving gaussian window function with a 10 fs width. The resulting smoothed function, $C_s(t)$, was then cutoff with the following criteria:

@@

where $f(t)$ is the debounced time-function that better represents the lifespans of cycles, eliminating the very brief discontinuities and excursions outside the bonding criteria that cause the rapid ``bouncing'' of the cyclic time-function, $C(t)$. Figure \ref{fig:debouncing} shows the original time-function of cycle formation and breaking, $C(t)$ (dashed black), the smoothed function, $C_s(t)$ (red), and the final debounced function, $f(t)$ (green).

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/SO-cycle-breakdown-with-cartoons-small.png}
		\caption{Cyclic hydrate structures form throughout the MD simulations involving the \suldiox~and one or more water molecules. Shown here are the different cycles by number of water (up to 4), and their occurrence rate as a percentage of the total simulation time. The far right part of the plot shows the contributions of the two types of triple-water cycles (see Figure \ref{fig:type-3-varieties}). The cycles had to meet the ``minimally-SO'' bonding criteria (at least one bond to the sulfur and one oxygen bond on the \suldiox) to be used in the analysis.}
		\label{fig:cyclic-breakdown}
	\end{center}
\end{figure}

@@

Knowing that the \suldiox~bound to a water surface is most likely in the ``SO'' bonding coordination, and also often taking part in some type of cyclic structure, how long does the cyclic hydrate form before breaking to an acyclic hydrate structure? To answer the questions of cyclic lifespans, a method was devised to define a lifetime of a cycle. For each trajectory, the coordinate data was analyzed to determine if a cyclic hydrate structure was formed based on the bonding distance criteria established earlier in this manuscript. A timeline was then produced where each timestep was given a value of 1 or 0 depending on if a \suldiox~hydrate bonding cycle was present or not, respectively. This resulted in a time-function, $C(t)$, similar in nature to a digital signal.

In an electro-mechanical system, a mechanical switch triggering an electrical signal often outputs a noisy signal that has a period of signal bounce before settling to a final value. This will appear as a rapid on-off cycling of the signal, and the problem is one of great concern in signal processing. Many mechanical, electrical, and software solutions have been devised for this problem of signal bounce. Analogously, the hydrate bonding cycles formed in the simulated system often undergo a period of time during formation, or before breaking, where the $C(t)$ function bounces before settling into a final value. The bounce in the function, manifested as a series of rapid switches between cycle presence and absence, signals a transition period due to the distortions of the bonds in the cyclic hydrates. We wish to find a function based on $C(t)$ that eliminates the brief oscillations during transitions. The resulting function, $f(t)$, will only contain information of whether a hydrate bonding cycle is present or absent, and none of the noisy oscillations of the transitions between the two states. $f(t)$ may then be used to calculate statistics about the cycle lifespans. The statistics thus calculated will no longer be skewed by the multiple short changes of state associated with the function bounce.

A representative portion of the resulting cycle time-function, $C(t)$, is plotted for one of the simulated trajectories shown as the dashed black line in Figure \ref{fig:debouncing}. At the far left of the plot the function is in the ``no cycle'' state indicating that a bonding cycle has not been detected, and then switches ``on'' as a cycle is found later in time. The cyclic structure is very dynamic, constantly moving and distorting, so any of the bonds forming the cyclic bonding structure are liable to break and reform quickly. This bouncing between states is manifested in Figure \ref{fig:debouncing} as a series of very sharp spikes in the $C(t)$ function lasting less than 10 fs each. The following procedure was used to debounce the time-function to disregard very brief moments when the cycle breaks or forms for less than 20 fs. The time-function, $C(t)$ was smoothed using a moving gaussian window function with a 10 fs width. The resulting smoothed function, $C_s(t)$, was then cutoff with the following criteria:

@@

where $f(t)$ is the debounced time-function that better represents the lifespans of cycles, eliminating the very brief discontinuities and excursions outside the bonding criteria that cause the rapid bouncing of the cyclic time-function, $C(t)$. Figure \ref{fig:debouncing} shows the original time-function of cycle formation and breaking, $C(t)$ (dashed black), the smoothed function, $C_s(t)$ (red), and the final debounced function, $f(t)$ (green).
